Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-12 eswc-2012/phdsymp.tex
simplify abstract
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@77 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{abstract}
Federation of semantic data on SPARQL endpoints will allow data to
remain distributed so that they can be controlled by local curators
and swiftly updated. It creates considerable performance problems,
however, that is intended in the suggested work to be addressed mainly
by computation and exposure of statistical digests to assist
selectivity estimation.

>>>>

\begin{abstract}
  Federation of semantic data on SPARQL endpoints will allow data to
  remain distributed so that they can be controlled by local curators
  and swiftly updated. There are considerable performance problems,
  intended in the suggested work to be addressed mainly by computation
  and exposure of statistical digests to assist selectivity
  estimation.
